Distrivia: A Distributed Trivia Game

### 2011-04-21 papers/phase-two/paper.tex
Minor edit, unversal to universally consistent.
Added Readme for Phase 2
Updated paper to reflect changes this week and to involve iPhone client

%\begin{abstract}
%In this paper we detail our initial idea for a distributed trivia game.
%We will explain general game play idea's as well as an example of the
%possible architecture for our system.
%\end{abstract}

\section {What We've Done}
Much of our system has been implemented and is in the debugging phase. The server apps and the web client are nearly complete with some revisions happening as necessary. The extent of what has been finished for each part of our system is explained below.
\subsection {Servers}
Currently, we have 6 servers running on Amazon's Elastic Compute Cloud \cite{aec}. One server is being used as a web-monitor
host. We are able to login to the web-monitor to see the status of all our
servers, databases, and load sharers. This will help us manage if the services
are running and allow us to track down any problems, if they arise. Three
servers are all running our server application and hosting the databases.
We also have two final servers that we have setup as hot spares in the event
of partial or total failure.
Each server contains the server application that responds to clients as well as
the Riak \cite{riak} databases. Riak auto-synchronizes the databases between the 5 servers.
Note that the hot spares are setup to be part of the database cluster so they
have a full copy of the database on hand, however they don't accept any reads
or writes directly. This allows for them to immediately be ready for read/writes in the event that the original servers are down.
With this configuration if we were to add a server, we would just need to update 
Riak and it would sync the databases to any additional servers as well. These servers,
therefore, all contain the same information. If any servers go down, the distributed
system would still run fine. We could have all servers go down except one and still
be reliably handling requests.

\subsection {Server Applications}
The server is currently almost feature complete, but still needs a lot of
testing. Client registration, and login are all supported. A client can
join a game, retrieve questions for that game, and answer questions. Both a
global leader board and individual per game leader board can also be requested. We recently refactored our API to be more universal. The servers and clients now work on a more consistent basis where the clients all expect the same information and use the same calls.

@@

\subsection {Clients}
Our focus for clients has been on a web-based client and an android application.
Both clients have most of the the workings completed. The web-based client will
be run from desktop platforms and laptop platforms. The android client will run
on any android phone running OS 2.1 or higher and does not use any unique services that require specific
hardware. The web client is nearly fully-functional. It currently can login/register
players, view leaderboards, join public games, and compete in public games. The android client has UI done for all the different activities. The android client can successfully register
and log players into games, view leaderboards, and join public games. We are actively adding features to both clients, daily.

@@

\section {What's Left}
\subsection {Server}
The server is nearly completed. The server application just needs to have some tweaks and further testing.
\subsection {Web Client}
A lot of the main features of the web client are completed.
However, there are still a few remaining features that need to be implemented.
While private games are implemented on the server, 
Also, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response,
alternatively it needs to be able to handle sending out two calls for the same request and not getting confused if it gets two back.
\subsection {Android}
We've started to thread the network calls to correctly register UI updates to the application. This is completed for most of the activities. There are really two big things left to implement on the android client: private games and competing in a round. Competing in a round is nearly finished, we just need to refresh the questions/answers and post the users answers to the server. Besides these two things, we just need to solidify the user interface, make it work with the back button with popping activities off the stack and other minor updates.

@@

Our system has two unique clients. One of them is designed for the Android platform as an app.
The other is a web client which is specifically being tested on Desktop and Laptop
browsers, however it may work on many hand held web browsers as well.

>>>>

%\begin{abstract}
%In this paper we detail our current progress on our distributed trivia game.
%We will explain what has been done so far, what we need to do, and how we
%have met the requirements for the project. We also discuss the architecture
%for our system.
%\end{abstract}

\section {What We've Done}
Much of our system has been implemented and is in the debugging phase. The server apps, web client, and android client are nearly complete with some revisions happening as necessary. We have also started development on an application for the iPhone platform. The extent of what has been finished for each part of our system is explained below.

\subsection{Architecture Overview }
\begin{figure}[h!]
  \centering
    \includegraphics[scale=0.4]{diagram.png}
   \caption{High level overview of the system}
 \end{figure}

\subsection {Servers}
Currently, we have 6 servers running on Amazon's Elastic Compute Cloud \cite{aec}. One server is being used as a web-monitor
host. We are able to login to the web-monitor to see the status of all our
servers, databases, and load sharers. This will help us manage if the services
are running and allow us to track down any problems, if they arise. Three
servers are all running our server application and hosting the databases.
We also have two final servers that we have setup as hot spares in the event
of partial or total failure.
Each server contains the server application that responds to clients as well as
the Riak \cite{riak} databases. Riak auto-synchronizes the databases between the 5 servers.
Note that the hot spares are setup to be part of the database cluster so they
have a full copy of the database on hand, however they don't accept any reads
or writes directly. This allows for them to immediately be ready for read/writes in the event that the original servers are down.
With this configuration if we were to add a server, we would just need to update 
Riak and it would sync the databases to any additional servers as well. These servers,
therefore, all contain the same information. If any servers go down, the distributed
system would still run fine. We could have all servers go down except one and still
be reliably handling requests.

\subsection {Server Applications}
The server is currently almost feature complete, but still needs a lot of
testing. Client registration, and login are all supported. A client can
join a game, retrieve questions for that game, and answer questions. Both a
global leader board and individual per game leader board can also be requested.
We recently refactored our API to be more universally consistent.
The servers and clients now work on a more consistent basis where the clients all expect the same information and use the same calls.

@@

\subsection {Clients}
Our focus for clients has been on a web-based client and an android application.
Both clients have most of the the workings completed. The web-based client will
be run from desktop platforms and laptop platforms. The android client will run
on any android phone running OS 2.1 or higher and does not use any unique services that require specific
hardware. Both clients are nearly fully-functional. They can, currently, login/register
players, view leaderboards, join public games, and compete in public games. We are actively adding features to both clients, daily.
We have also started development on an iPhone application for distrivia. This client does not yet communicate with the server, but 
it does implement nearly all the views seen in the other clients. We have been setting up the network communication for the iPhone
platform as well.

@@

\section {What's Left}
\subsection {Server}
The server is nearly completed. The server application just needs to have some tweaks and further testing.
\subsection {Web Client}
A lot of the main features of the web client are completed.
However, there are still a few remaining features that need to be implemented.
While private games are implemented on the server, 
Also, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response,
alternatively it needs to be able to handle sending out two calls for the same request and not getting confused if it gets two back.
\subsection {Android}
Private gameplay is the largest thing left for the android client. Besides this we've just been fixing bugs and cleaning up the UI.
\subsection {iPhone}
The iPhone application just started development in the last couple days. We have built most of the UI but need to connect all of the actions
to the server. We will need to implement everything, including login/registration, joining public/private games, viewing leaderboards,
and competing in rounds.

@@

Our system has three unique clients. One of them is designed for the Android platform as an app.
Another is designed for the iPhone platform as a native app.
The third is a web client, which is specifically being tested on Desktop and Laptop
browsers, however it may work on many hand held web browsers as well.
